Verifying Demonstrations

### 2018-06-11 paper/DB-anon-cred.tex
edited and commented until end of building blocks

\ProvideDocumentCommand{\PPK}{o o}{\ensuremath{%
    \operatorname{PPK}%
    \IfValueT{#1}{%
      \IfValueTF{#2}{%
        \mleft\{\mleft(#1\mright) : #2\mright\}%
      }{%
        \mleft\{#1\mright\}%
      }%
    }%
  }}

One protocol exists in the literature that provides \acp{PPK} with most of the desired properties described previously, ProProx~\cite{ProProx}\footnote{Note that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for shorter notation.}.
However, ProProx is not secure against a malicious verifier and does not provide \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = \alpha^2]\)) while in our context, we need \iac{PPK} protocol for discrete logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\)).
To realize this, we will now introduce such a protocol in order to enable us to have \ac{DB} anonymous credentials.

\NewScheme{\DBS}{DBS}
\NewAlgorithm{\DBSprove}{\DBS.\!Prove}
\NewAlgorithm{\DBSverify}{\DBS.\!Verify}

\emph{Reattempting a distance-bounding Schnorr protocol.}
In the original \ac{DB} paper by \citet{DistanceBounding}, one of the distance-bounding protocol is based on the Schnorr identification scheme~\cite{Schnorr}.
However, this \ac{DB} Schnorr protocol was shown to be prone to distance hijacking~\cite{DistanceHijacking}, in addition of also not being secure against terrorist fraud either.
We now propose another way to turn the Schnorr protocol into a public-key \iac{DB} protocol which is secure against \ac{DBMF}, \ac{DBDF}, \ac{DBDH}, \ac{DBTF} and an impersonating verifier.

We present the protocol in \cref{SchnorrFigure}.
The main difference with the original Schnorr protocol is that the prover commits to one random value but the verifier sends two challenges.
The verifier presents to the prover which commitments and challenges to use during the \ac{DB} phase.

@@

The intuition behind the protocol security is as follows.
To achieve malicious-verifier zero-knowledge, choose \(k\) logarithmically with respect to the security parameter \(\lambda\) and repeat the protocol until the knowledge error is small enough.
This will actually also decrease the success probability of \iac{DBMF} adversary in the \ac{DB} step.
Indeed, the \ac{DBMF} adversary does not know which challenge the verifier will use, thus there is a \(1/2\) probability that the \ac{DBMF} adversary will guess it correctly.
The prover will only provide one of the responses: even if the adversary re-runs the protocol with the same challenges, the randomly chosen \(\rho_0, \rho_1\) will have changed --- which thus yields another \(R_b\) in the end of the protocol.
A sequential repetition of protocol will decrease this probability.

@@

The protocol is \ac{DBTF}-resistant, indeed if the malicious prover gives both responses to the adversary, the adversary can compute his secret key.
This follows from the fact that it is \iac{ZKPK}, which means there is an extractor that can leak the secret.
The protocol is also secure against distance hijacking due to the fact that it is the authenticated bitstring that is used during the \ac{DB} phase, not the challenge bitstring as in the protocol of Brands-Chaum.

>>>>

One protocol exists in the literature that provides \acp{PPK} with most of the 
desired properties described previously, ProProx~\cite{ProProx}\footnote{Note 
  that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for 
  shorter notation.}.
However, ProProx is not secure against a malicious verifier and does
not \sonja{I think ``not'' should be removed} provide \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = \alpha^2]\)) while in our context, we need \iac{PPK} protocol for discrete logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\)).
To realize this, we will now introduce such a protocol in order to enable us to have \ac{DB} anonymous credentials.

\emph{Reattempting a distance-bounding Schnorr protocol.}
In the original \ac{DB} paper by \citet{DistanceBounding}, one of the distance-bounding protocol is based on the Schnorr identification scheme~\cite{Schnorr}.
However, this \ac{DB} Schnorr protocol was shown to be prone to distance hijacking~\cite{DistanceHijacking}, in addition to not being secure against terrorist fraud.
We now propose another way to turn the Schnorr protocol into a
public-key \iac{DB} protocol which is secure against \ac{DBMF},
\ac{DBDF}, \ac{DBDH}, \ac{DBTF} and an impersonating
verifier. \sonja{contrast with \ac{DBIF}}

We present the protocol in \cref{SchnorrFigure}.
The main difference to the original Schnorr protocol is that the prover commits to one random value but the verifier sends two challenges.
The verifier presents to the prover which commitments and challenges to use during the \ac{DB} phase.

@@

The intuition behind the protocol security is as follows.
To achieve malicious-verifier zero-knowledge, choose \(k\) logarithmically with respect to the security parameter \(\lambda\) and repeat the protocol until the knowledge error is small enough.
This will actually also decrease the success probability of \iac{DBMF} adversary in the \ac{DB} step.
Indeed, the \ac{DBMF} adversary does not know which challenge the verifier will use, thus there is a \(1/2\) probability that the \ac{DBMF} adversary will guess it correctly.
The prover will only provide one of the responses: even if the adversary re-runs the protocol with the same challenges, the randomly chosen \(\rho_0, \rho_1\) will have changed --- which thus yields another \(R_b\) at the end of the protocol.
A sequential repetition of the protocol will decrease this probability.

@@

The protocol is \ac{DBTF}-resistant, indeed if the malicious prover gives both responses to the adversary, the adversary can compute his secret key.
This follows from the fact that it is \iac{ZKPK}, which means there is an extractor that can leak the secret.
The protocol is also secure against distance hijacking due to the fact
that it is the authenticated bitstring that is used during the \ac{DB}
phase, not the challenge bitstring as in the protocol of Brands-Chaum.
\sonja{this is analysis but not in the analysis section}

### 2018-06-11 paper/SystemModel.tex
edited and commented until end of building blocks

\emph{Defining the concept of protest.} 
To be able to estimate the participation count for a protest, we first need to define this concept and which quantity should be counted.
Let us start by considering some examples.
During the demonstrations against the South Korean president in Seoul in 2016
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{t}he rallies stretch\textins{ed} from midday to late night --- some people stay\textins{ed} for several hours, others just several minutes%
}.
These rallies were all in the same location in the capital city and repeated every weekend for the duration of a few weeks.
The Women's Marches in 2017~\cite{2017WomensMarchesInUS}, on the other hand, occurred in parallel in many locations.
We also have the Venezuelan demonstrations in 2017 in which \blockcquote{2017VenezuelaProtestFrequency}{%
  anti-government demonstrators have staged daily protests across Venezuela%
} while
\blockcquote{AlJazeeraOnVenezuela2017}{%
  pro-government workers sang and danced as they staged a rival march to show their support for the president's controversial plan to rewrite the constitution%
}.
Generalizing from these examples, the minimal common part is the cause,%
\label{CauseIsTheCommonDenominator} while the location (or area) considered 
varies over time.

For the rest of the paper, we will refer to the organizer as Alice.
Assume that the objective of Alice is to count everyone who participated at any time and in any of the locations~\cite{2016DemonstrationsInSeoul}\footnote{Remark that the objective does not necessarily align with the definition of the police whose interest could be to determine the maximum crowd at any point in time to deploy enough personnel for crowd-control.}.
% cause identifier
Formally, we define a protest as an event that is uniquely identified by its cause \(\cid\), its time interval \(t\) and its location (area) \(l\).
More specifically, we will use the following definition.

@@

Our protocol relies on \emph{witnesses} to certify and associate the proof to the location by creating a \emph{proof share}.
A witness is only allowed to create one proof share per protester to avoid the risk of inflation.
Note that a participant to a protest can take the role of a protester but also act as witness for other protesters.
%Seb: the sentence below is not very clear, it should be rephrased to make it clearer
The participation proof and its proof shares are stored in a set, as there should be only unique proof shares.

@@

\begin{definition}[Participation proof]%
  \label{DefParticipationProof}\label{DefParticipationProofs}
  A \emph{participation proof} of a protester with pseudonym \(\pid\) who participates in a protest \(\prtst = \{ (\cid, t_i, l_i) \}_i\) is the set
  \begin{multline}
    \nonumber
    \prf_{\pid, \prtst} =
    \left\{ \psh = (\cid, t, l, \pid, \wid)\in \pshs \mid
      \exists \sprtst\in \prtst\colon \psh\sqsubseteq \sprtst \right\}
  \end{multline}
  of all proof shares with the same protester and protest identifiers, witnessing time interval \(t\) and location \(l\) is within those of the protest.
  We denote by \(\prfs\) the set of all proofs.
\end{definition}

@@

The strength function \(\str\) can be used to regulate the trust in the participation count estimated.
One example would be for \(\str\) to return the number of unique witnesses and thus let \(\theta\) to be the threshold of the number of required witnesses.
%Seb: we should define clearly the different type of witnesses (for instance unique and trusted witnesses)
Another possibility would be to also have a particular type of witnesses, called trusted witnesses, participating to the protest. 
For instance, the role of the trusted witness could be taken by Jane, the independent journalist. 
In this situation, the strength function could be defined with respect to the number of proof shares issued by trusted witnesses and set \(\theta = 1\) to require at least one proof share issued by a trusted witness.

>>>>

%\emph{Defining the concept of protest.} 
To be able to estimate the participation count for a protest, we first need to define this concept and which quantity should be counted.
Let us start by considering some examples.
During the demonstrations against the South Korean president in Seoul in 2016
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{t}he rallies stretch\textins{ed} from midday to late night --- some people stay\textins{ed} for several hours, others just several minutes%
}.
These rallies were all in the same location in the capital city and repeated every weekend for the duration of a few weeks.
The Women's Marches in 2017~\cite{2017WomensMarchesInUS}, on the other hand, occurred in parallel in many locations.
We also have the Venezuelan demonstrations in 2017 in which \blockcquote{2017VenezuelaProtestFrequency}{%
  anti-government demonstrators have staged daily protests across Venezuela%
} while
\blockcquote{AlJazeeraOnVenezuela2017}{%
  pro-government workers sang and danced as they staged a rival march to show their support for the president's controversial plan to rewrite the constitution%
}.
Generalizing from these examples, the minimal common part is the cause,%
\label{CauseIsTheCommonDenominator} while the location (or area) considered 
varies over time.

For the rest of the paper, we will refer to the organizer as Alice.
Assume that the objective of Alice is to count everyone who
participated at any time and in any of the
locations~\cite{2016DemonstrationsInSeoul} \sonja{commented out for
  repetition: %\footnote{Note that the objective does not necessarily
              %align with the definition of the police whose interest
              %could be to determine the maximum crowd at any point in
              %time to deploy enough personnel for crowd-control.
}.
% cause identifier
Formally, we define a protest as an event that is uniquely identified by its cause \(\cid\), its time interval \(t\) and its location (area) \(l\).
More specifically, we will use the following definition.

@@

Our protocol relies on \emph{witnesses} to certify and associate the proof to the location by creating a \emph{proof share}.
A witness is only allowed to create one proof share per protester to avoid the risk of inflation.
Note that a participant of a protest can take the role of a protester but also act as witness for other protesters.
%Seb: the sentence below is not very clear, it should be rephrased to make it clearer
The participation proof and its proof shares are stored in a set, as there should be only unique proof shares.

@@

\begin{definition}[Participation proof]%
  \label{DefParticipationProof}\label{DefParticipationProofs}
  A \emph{participation proof} of a protester with pseudonym \(\pid\) who participates in a protest \(\prtst = \{ (\cid, t_i, l_i) \}_i\) is the set
  \begin{multline}
    \nonumber
    \prf_{\pid, \prtst} =
    \left\{ \psh = (\cid, t, l, \pid, \wid)\in \pshs \mid
      \exists \sprtst\in \prtst\colon \psh\sqsubseteq \sprtst \right\}
  \end{multline}
  of all proof shares with the same protester and protest identifiers, witnessing time interval \(t\) and location \(l\) within those of the protest.
  We denote by \(\prfs\) the set of all proofs.
\end{definition}

@@

The strength function \(\str\) can be used to regulate the trust in the participation count estimated.
One example would be for \(\str\) to return the number of unique witnesses and thus let \(\theta\) to be the threshold of the number of required witnesses.
%Seb: we should define clearly the different type of witnesses (for instance unique and trusted witnesses)
Another possibility would be to also have a particular type of witness, called trusted witness, participating in the protest. 
For instance, the role of the trusted witness could be taken by Jane, the independent journalist. 
In this situation, the strength function could be defined with respect to the number of proof shares issued by trusted witnesses and set \(\theta = 1\) to require at least one proof share issued by a trusted witness.
